In this section we define \emph{locally-verifiable distributed SNARGs} ($\LVDSNARG$s) and show how to construct them for distributed languages in
$\PP$ from RAM SNARGs.
\TODO{Put the NP stuff in the appendix and refer it}

A \textcolor{red}{$t$-locally} verifiable distributed SNARG consists of the following algorithms.
\TODO{Discuss the transformation from $\mathbin{\color{red}t}$-round verifier to just a verifier that receives $\pi_{N^{\mathbin{\color{red}t}}(v)}$.}

\begin{itemize}
    \item $\Gen(1^\secpar, n)\to \var{\crs}$: a randomized algorithm that takes as input a security parameter $1^\secpar$ and a graph size $n$, and outputs a common reference string $\var{\crs}$.
    \item $\Pro(\var{\crs}, G, w)\to \{\pi_v\}_{v\in V(G)}$: takes a $\var{\crs}$ obtained from $\Gen(1^{\secpar}, n)$, a graph $G$ on $n$ nodes, and possibly a witness $w$ of length $\poly(n)$ (which may be empty, e.g., for languages in $\PP$), 
    \footnote{For languages in $\PP$, we'll ommit $w$ from $\Pro$'s inputs.} 
    and outputs a list of proofs $\{\pi_v\}_{v\in V(G)}$, one for each node $v \in G$.
    \item $\Ver(\var{\crs}, v, N^{\mathbin{\color{red}t}}(v), \pi_v, \pi_{N^{\mathbin{\color{red}t}}(v)} )\to \{0,1\}$: takes a common reference string $\crs$ obtained from $\Gen(1^{\secpar}, n)$, a UID $v$, a list of ${\mathbin{\color{red}t-}}$neighbors $N(v)$, a proof $\pi_v$, and the proofs of the ${\mathbin{\color{red}t-}}$neighbors, $\pi_{N^{\mathbin{\color{red}t}}(v)} = \set{ \pi_u : u \in N^{\mathbin{\color{red}t}}(v) }$, 
    \footnote{For simplicity, we follow the original design of proof labeling schemes~\cite{korman2005proof}, where neighbors only exchange their certificates with their immediate neighbors. The model can be generalized to allow for more general verification procedures.} 
    and outputs an acceptance bit. 
    \TODO{Do we need this $t$ thing}
\end{itemize}







%\rc{this should be in a definition environment}
%\Enote{I'm not sure... }

\begin{definition}\label{defSDarg}
%Let $\Lan$ and $\calR$ be an $\NP$ language and a compatible relation on graphs, such that $G \in \calL$ iff there exists a witness $w$ such that $(G,w) \in \calR$.
Let $\Lan$ be a distributed language.
A \emph{succinct distributed argument} for $\Lan$, %and $\calR$,
denoted $(\Gen, \Pro, \Ver)$, satisfies the following properties:
\vspace{-1ex}
\paragraph{Completeness}  For $(G,x)\in \calL$,
\begin{gather*}
    \prb
    {
    	\forall v \in V(G):\\
	    \Ver(\crs, v, x(v), N(v), \pi_v, \pi(N(v))) = 1
	}
	{
    \crs \leftarrow \Gen(1^\secpar, n) \\
    \set{ \pi_v }_{v\in V(G)} \leftarrow \Pro(\var{\crs}, G, x)
    }
    = 1
    .
\end{gather*}
\paragraph{Soundness}
For any poly-size algorithm $\Pro^*$ %, and $G\notin \Lan$,
there exists a negligible function $\epsilon(\cdot)$ such that
\begin{gather*}
    \prb
    {
    (G,x)\notin \Lan \\
    \wedge\ \forall v\in V(G) :\\
    \quad \Ver(\var{\crs}, v, N^{\mathbin{\color{red}t}}(v), \pi_v, \pi_{N^{\mathbin{\color{red}t}}(v)} ) = 1
    }
    {
    \var{\crs} \leftarrow \Gen(1^\secpar, n) \\
    ( G, x, \{\pi_v\}_{v\in V(G)}) \leftarrow \Pro^*(\var{\crs}, 1^\secpar, 1^n)
    } \leq \epsilon(\secpar)
    .
\end{gather*}
\paragraph{Succinctness} The $\crs$ and the proof $\pi$ are of length at most $\poly(\secpar, \log n)$.

\paragraph{Efficiency.} $\Ver$ runs in time $\poly(\lambda, |\pi|) = \poly(\lambda, \log n)$,
and $\Pro$ runs in time $\poly(\lambda, n)$.
\end{definition}
